Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-20 reports/manuscript/paper.tex
Adds some information about inference vs. prediction.

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
 We approach differences between individuals through a ``decoding'' lens:
We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling
This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss}).

>>>>

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}.
For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with tract profiling.

### 2021-04-20 reports/manuscript/paper_changes.tex
Adds some information about inference vs. prediction.

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{ We approach differences between individuals through a ``decoding'' lens:}
We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.

>>>>

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{Unlike many previous analyses of white matter (e.g., using TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}), which focus on classical inference of the differences between groups or individuals in terms of their white matter properties, the focus of the present work is on the combination of features that facilitate accurate prediction of the individual differences in a \emph{phenotype}}.
\added{For example, an accurate prediction of which individuals in a group have a particular disease, or a prediction of their age with small error. The distinct goals of \emph{inference} and \emph{prediction} are not necessarily incongruent, but can sometimes be in tension \cite{Bzdok2020-sd}. This distinction is also similar to the distinction between ``encoding'' and ``decoding'' used in the functional MRI literature \cite{Naselaris2011-ss}. In the present work}, we predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}.
